Risk Perceptions for Wearable Devices

### 2015-04-15 tex-inputs/results-openended.tex
tweaks to open-ended

%!TEX root = ../paper.tex
\subsection{Open-Ended Concerns for Wearables}
We captured participants' general reactions to wearable devices as a whole by asking the following open-ended question:

\textit{What do you think are the most likely risks associated with wearable devices?}\\[-.5cm]

@@

In addition to privacy and security in the general sense, significant concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware). Other concerns were orthogonal to privacy, such as long-term health effects caused from wearing the device such as cancer from EMF waves (Health), safety hazards from wearing the device, such as distractions that cause car accidents (Safety), resulting changes in social behaviors, such as dependence on devices or spending less time with loved ones (Social Impact), the high financial cost of buying, replacing, or caring for the device (Financial).

>>>>

%!TEX root = ../paper.tex
\subsection{Open-Ended Concerns for Wearables}
We captured participants' reactions to wearable devices as a whole by asking the following open-ended question:

\begin{quotation}
\noindent
\textit{What do you think are the most likely risks associated with wearable devices?}
\end{quotation}

@@

In addition to privacy and security in the general sense, significant concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware). Other orthogonal concerns included long-term health effects caused from wearing the device such as cancer from EMF waves (Health) and safety hazards from wearing the device, such as distractions that cause car accidents (Safety). Interestingly, participants were also concerned with resulting changes in social behaviors, such as dependence on devices or spending less time with loved ones (Social Impact).
